Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
update

$$
p_{ij} = \frac{w(t_i - t_j)}{\sum_{i \neq k} }
$$
## Results
[What methods/models are best]
[What condition(s) does each method/model work well/poorly]
[Conclusion about dataset]

@@

[TK: Beta values]
Fitting our Bayesian model, which extends the method of Thompson et. al, values of beta were estimated for temperature, relative humidity, Gross Domestic Product (GDP) and population density, respectively.  Thus, our model estimates $\beta^T = [,,,,]$ in
$$ R_i(t) = \exp\left( \theta(t) + \lambda_i + \mathbf{\beta}^T x_i(t) + \varepsilon_i(t) \right)$$
Note that each feature's data is standardized to mean 0 and variance 1.

The model indicates that higher temperatures are observed with lower $R_0$ values, and higher GDP is observed with higher $R_0$ values, while relative humidity and population density have $R_0$ close to zero.

### Posterior of Lambda, location-dependent adjustment to log(R)

- $\lambda$ is an adjustment to the model based on the location you're in.
### Climate-Independent Basic R, by Date

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot5.png}
\end{center}
- R_0 is high in early phases, with an early spike on February 27, potentially due to increased in testing, which captures cases before.
- Climate-independent means ignores local climates, and produces an aggregate result.

@@

- local, no longer climate independent.

### Epsilon, Idiosyncratic adjustment to log(R)
\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot11.png}
\end{center}

@@

>>>>

$$
p_{ij} = \frac{w(t_i - t_j)}{\sum_{i \neq k} }
$$

## Results

[What methods/models are best]
[What condition(s) does each method/model work well/poorly]
[Conclusion about dataset]

### Posterior Estimates

@@

[TK: Beta values]
Fitting our Bayesian model, which extends the method of Thompson et. al, values
of beta were estimated for temperature, relative humidity, Gross Domestic
Product (GDP) and population density, respectively. The mean estimate of $\beta^T$ is

$$ \beta^T = [-0.23198507 -0.05391226  0.26336295 -0.03586852] $$

in the overall model for $R$

$$ R_i(t) = \exp\left( \theta(t) + \lambda_i + \mathbf{\beta}^T x_i(t) + \varepsilon_i(t) \right)$$
Note that each feature's data is standardized to mean 0 and variance 1.

The model indicates that higher temperatures are observed with lower $R$ values,
and higher GDP is observed with higher $R$ values, while relative humidity and
population density have close to no effect on $R$. Because of the confidence
intervals, we are fairly confident of the directional correctness of this
relationship for temperature and for GDP per capita.

### Climate-Independent Basic R, by Date

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot5.png}
\end{center}

$R$ is high in early phases, with an early spike on February 27, potentially due
to increases in testing, which means the data (and hence the model) has
underestimated the number of infectious cases compared to the ground truth.
This result is aggregate across the entire nation and is net of any contribution
to national weather changes.

@@

These plots show the estimated $R$ values in each province computed through the
samples from the MCMC. An important observation is that the confidence intervals
for many provinces are very wide, because those provinces have relatively little
data. However, one strength of our model is that no weighting on results from
each province needs to be manually done. The data from larger provinces is
automatically more important because the Poisson likelihood function returns
smaller results as the rate parameter increases.

We have also analyzed the $\lambda$ and $\varepsilon$ parameters of the model,
but because these are not as important, see the Appendix for plots and analysis.

@@

### Posterior of $\lambda$, location-dependent adjustment to $log(R)$

$\lambda$ is an adjustment to the model based on the location. What we observe
from the distribution of $\lambda$ is that some locations have much more
certainty in how they deviate from the mean than others. This can be explained
by the unequal distribution of cases across provinces; provinces with more cases
lend themselves to more accurate estimation of $R$.

### Epsilon, idiosyncratic adjustment to log(R)

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot11.png}
\end{center}
